\papertitle

### 2014-03-20 final-report/paper.tex
Fix abstract

We propose \system, a visualization tool that helps database developers
explore and understand query execution and data movement in a distributed
database management system (DDBMS). \system provides quick insight into common
problems such as data skew or performance bottleneck by leveraging
visualization techniques to present: (1) data flow between query segments and
between workers, (2) query execution and operator dependencies, (3) cluster
utilization, (4) network utilization.

>>>>

We propose \system, a visualization tool that helps database developers
explore and understand query execution and data movement in a distributed
database management system (DDBMS). \system provides quick insight into common
problems such as data skew or performance bottleneck by leveraging
visualization techniques to present: (1) data flow between query operators and
between workers, (2) query execution and operator dependencies, (3) cluster
utilization, (4) network utilization.
